### 2015-09-14 vmcai-2016-tex/abstract.tex
First 3 sections...

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state. A fundamental problem
with using these guarded value sets is the creation of test inputs for
programs accepting symbolic reference input parameters. Although
several solutions have been proposed, none have been proven to be
sound and complete with respect to the properties provable by
generalized symbolic execution (GSE). This work presents a method for
initializing reference inputs in a symbolic input heap using guarded
value sets that exactly preserves GSE semantics. A correctness proof
for the initialization scheme is provided, as well as the results of
an empirical evaluation of a proof-of-concept implementation. The
initialization technique can be used to ensure that guarded value set
based symbolic execution engines operate in a provably correct manner
with regards to symbolic references.

>>>>

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state. A fundamental problem
with using these guarded value sets is the creation of test inputs for
programs accepting symbolic reference input parameters. Although
several solutions have been proposed, none have been proven to be
sound and complete with respect to the properties provable by
generalized symbolic execution (GSE). This work presents a method for
initializing reference inputs in a symbolic input heap using guarded
value sets that exactly preserves GSE semantics. A correctness proof
for the initialization scheme is provided, as well as the results of
an empirical evaluation of a proof-of-concept implementation showing a real increase in the size and number of analyzed heaps compared to existing GSE representations. The
initialization technique can be used to ensure that guarded value set
based symbolic execution engines operate in a provably correct manner
with regards to symbolic references.

### 2015-09-14 vmcai-2016-tex/intro.tex
First 3 sections...

This paper includes a proof that symbolic initialization is sound and
complete with respect to properties provable by GSE. Such a result is
important because it means that symbolic initialization can be used to
create input heaps for other analyses in a way that is provably
correct with regards to GSE: there are no missing heaps and there are
no extra heaps.

>>>>

This paper includes a proof that symbolic initialization is sound and
complete with respect to properties provable by GSE. Such a result is
important because it means that symbolic initialization can be used to
create test inputs for other analyses in a way that is provably
correct with regards to GSE: there are no missing heaps and there are
no extra heaps.

### 2015-09-14 vmcai-2016-tex/lazy.tex
First 3 sections...

\section{GSE}
\label{app:gse}
Classical GSE and its variants all subscribe to the same ideal: an uninitialized object may be lazily initialized
in a non-deterministic way to null, a new instance of the object, or an to
an object of the same type also initialized lazily (i.e., the \emph{input heap}) \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. The
non-determinism creates branches in the execution
tree during state space exploration. GSE semantics are defined here to give insight to symbolic initialization and support the proof that it preserves GSE behaviors.

The rules for classical GSE using the symbolic heap are in
\figref{fig:lazyInit} for lazy initialization: NULL, new, and alias. Fresh references and locations strictly increase so it is possible to minimize over a set to find the first created. References are partitioned to support latter proofs: $\mathrm{init}_\cfgnt{r}()$ for the input
  heap
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
    literals}.
  In general, as shown in the next section,
  only input heap references appear in constraints to express potential aliasing, and only stack references can appear in environments, expressions, or continuations.  Finally, the \emph{isInit} is true for initialized references from the input heap (i.e., potential aliases).

How the lazy
initialization is used is defined in \figref{fig:lazy}. Specifically,
the field-access rule in \figref{fig:lazy} uses initialization,
$\rightarrow_I^*$, to ensure the accessed field is
instantiated. Initialization in generalized symbolic execution never
happens for more than one object on any use of $\rightarrow_I^*$:
$\Lambda$ is either empty or contains exactly one location. This property is an artifact of how GSE case spits when it instantiates: each choice is a new unique heap. The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization.

The $\rgse$ relation defined in \figref{fig:lazy} is a union over branching points on control flow
to support the final proof of the existence of a
bisimulation. Although it is apparent that there is non-determinism in
initialization at the first reference access partitioning the search space, control flow branches at comparisons and NULL-exceptions. This property is reflected in the composition of $\rgse$.

>>>>

\section{GSE}
\label{app:gse}
GSE semantics are defined here to give insight to the new symbolic initialization approach and support the proof that the new approach preserves GSE behaviors. GSE and its variants have the same non-deterministic choice given a reference to an uninitialized object; that reference can point to null, a new instance of an object with the correct type, or to an object of the same type that has been instantiated previously by GSE \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. The objects instantiated for new instances are referred to as the \emph{input heap}. Only these objects comprise the potential alias set when GSE encounters references to uninitialized objects. In general, the GSE search space branches at uninitialized objects, and the number of branches depends on the size of the input heap.

The lazy initialization rules for GSE on the symbolic heap are in
\figref{fig:lazyInit}: NULL, new, and alias. The rules rely on fresh references and locations that strictly increase so it is possible to minimize over a set to find the first created. Further, references are partitioned to support latter proofs: $\mathrm{init}_\cfgnt{r}()$ for the input
  heap
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
    literals}.
  In general, as shown in the next section,
  only input heap references appear in constraints to express potential aliasing, and only stack references appear in environments, expressions, or continuations.  Finally, the \emph{isInit} function is true for initialized references from the input heap (i.e., potential aliases).

How the lazy
initialization is used is defined in \figref{fig:lazy}. Specifically,
the field-access rule in \figref{fig:lazy} uses initialization,
$\rightarrow_I^*$, to ensure the accessed field is
instantiated. Initialization in generalized symbolic execution never
happens for more than one object on any use of $\rightarrow_I^*$:
$\Lambda$ is either empty or contains exactly one location. This property is an artifact of how GSE case spits when it instantiates: each choice is a new unique heap. The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization. In particular, there is no branching in the search space on reference compare for GSE because references point to a single location. The new symbolic initialization using guarded value sets in the next section changes this behavior.

The $\rgse$ relation defined in \figref{fig:lazy} is a union over branching points on control flow
to support the final proof of the existence of a
bisimulation. Although it is apparent that there is non-determinism in
initialization at the first access to an uninitialized reference, control flow branches at comparisons and NULL-exceptions. This property is reflected in the composition of $\rgse$.

### 2015-09-14 vmcai-2016-tex/summary-heap.tex
First 3 sections...

\section{A Symbolic Heap}
A \emph{symbolic heap}, as defined in this work, is a tuple
$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map}
$\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment}
$\eta$ are partial functions, and the~\emph{path condition} $\phi$ is
a predicate over the program variables. Given reference $r$,
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
in the heap associated with $r$. The constraint associated with each
location is a guard representing the conditions under which the
associated reference maps to the given location. By definition, any
location appears at most once in any given value set. Unions of value
sets containing the same location are resolved by forming a
disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
location-field pair in the heap.

@@

Conceptually, the symbolic heap may be thought of as a bipartite
graph. \figref{fig:exampleHeap} shows an example symbolic heap
graph. References are represented by circles and locations are
represented by squares. Arrows leaving references correspond to the
guarded value sets returned by the $\cfgnt{L}$ function, and arrows
leaving the squares correspond to the $\cfgnt{R}$ function. The
reference $\cfgnt{r}_1$ has has two members in it guarded value set,
so the location pointed to by $\cfgnt{r}_1$ depends on its aliasing
relationship to $\cfgnt{r}_0$.

@@

A program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. For simplicity in presentation, booleans are the only primitive type, 
classes have only non-primitive fields, and methods have a single
parameter. Expressions, $\cfgnt{e}$, include statements, and they use
'$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate
comparison.  The dot-operator for field access is replaced by
'$\cfgt{\$}$', and the dot-operator for method invocation is replaced
by '$\cfgt{@}$'. There is no
explicit return statement; rather, the value of the last expression is
used as the return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap,
$\cfgnt{r}$, or any of the special values shown
in~\figref{fig:syntax}(a).  Only type correct programs are given as
input to the machine.

>>>>

\section{A Symbolic Heap}
A \emph{symbolic heap}, as defined in this work, is a tuple
$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map}
$\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment}
$\eta$ are partial functions, and the~\emph{path condition} $\phi$ is
a predicate over the program variables. Given reference $r$ in the heap,
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
associated with $r$. The constraint associated with each
location is a guard representing the conditions under which the
associated reference maps to the given location. By definition, any
location appears at most once in any given value set. Unions of value
sets containing the same location are resolved by forming a
disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
location-field pair in the heap.

@@

Conceptually, the symbolic heap may be thought of as a bipartite
graph. \figref{fig:exampleHeap} shows an example symbolic heap
graph. References are represented by circles and locations are
represented by squares. Arrows leaving references correspond to the
guarded value sets returned by the $\cfgnt{L}$ function, and arrows
leaving the squares correspond to the $\cfgnt{R}$ function. The
reference $\cfgnt{r}_1$ in the figure has two members in its guarded value set,
so the location pointed to by $\cfgnt{r}_1$ depends on its aliasing
relationship to $\cfgnt{r}_0$.

@@

A program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. For simplicity in presentation, booleans are the only primitive type, 
classes have only non-primitive fields, and methods have a single
parameter. Expressions, $\cfgnt{e}$, include statements, and they use
'$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate
comparison.  The dot-operator for field access is replaced by
'$\cfgt{\$}$', and the dot-operator for method invocation is replaced
by '$\cfgt{@}$'. There is no
explicit return statement; rather, the value of the last expression is
used as the return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap,
$\cfgnt{r}$, or any of the special values shown
in~\figref{fig:syntax}(a).
